Fully Automatic Loop-free Program Synthesis by Bounded Model Checking

### 2013-10-09 paper/paper.tex
First changes to word width parameter

@@

\subsection{Word Width: $w$}
It is often the case that a program which satisfies the specification will
continue to satisfy it regardless of the word width of the machine it is
implemented on.  For example, the program in Fig.~\ref{fig:bitvector-program}
isolates the least-significant bit of an 8-bit word, but it will also
isolate the least-significant bit of a 32-bit word or indeed of a word of
any size.

>>>>

\subsection{Word Width: $w$}
An $\mathcal{L}$-program runs on a virtual machine (the $\mathcal{L}$-machine) that
has its own set of paramters.  The only parameter that we care about is
the \emph{word width} of the $\mathcal{L}$-machine, that is the number of bits
in each internal register and immediate constant.  This parameter is denoted by
$w$.  The size of the final SAT problem generated by {\sc cbmc} scales
approximately linearly with $w$, since each intermediate C variable corresponds
to $w$ propositional variables.

It is often the case that a program which satisfies the specification will
continue to satisfy it regardless of the word width of the machine it is
implemented on.  For example, the program in Fig.~\ref{fig:bitvector-program}
isolates the least-significant bit of an 8-bit word, but it will also
isolate the least-significant bit of a 32-bit word or indeed of a word of
any size.

@@
